### 2017-03-18 papers.tex
Update master paper list for 2017
Although we haven't yet settled on the new track numbering scheme

\addproceedings{ToC About Proceedings! Have We Got Papers for You!}

\addtrack{Half-track}{Crypticography}
\addpaper
	{Cryptographically secure page numbering in \LaTeX}
	{William Gunther and Brian Kell}
	{cryptography, hashing, LaTeX, macros, page numbers, security, SHA-256}
	{SIGBOVIK_2016_paper_18}
	{0cm}
	{\includegraphics[width=1in]{eval}}
\addreview{paper18eval}{0cm}
\addpaper
	{Random seed generation}
	{Alexander R.\ Frieder}
	{random, seed, encryption, complexity, am, I, even, supposed, to, fill, this, out, what, amI, doing, ?}
	{SIGBOVIK_2016_paper_1}
	{0cm}
	{}

\addtrack{Full track}{Safety Schools of Thought}
\addpaper
	{Reducing the trusted constituent base with the LCF approach: Hillary, the next 700 elections}
	{Brandon Bohrer, Sol Boucher, and Jos Valdivida}
	{illogical, logic, Hillary, elections, congressional, fuckery, robustness, constituents, unrest, pork-barreling, curtain-closing}
	{SIGBOVIK_2016_paper_25}
	{0cm}
	{}
\addpaper
	{Unprl: Nuprl proof re-evaluation logic}
	{Ryan Kavanagh}
	{proof assistant, Nuprl, The Wizard of Oz, artificial artificial intelligence}
	{SIGBOVIK_2016_paper_11}
	{0cm}
	{}
\addpaper
	{Type-safe friends will never hurt you}
	{Brandon Bohrer}
	{friendship logic, friends, office mates, Cwelf}
	{SIGBOVIK_2016_paper_9}
	{0cm}
	{}
\addreview{review9}{0cm}

\addtrack{Rototiller track}{Overcomplexity Theory}
\addpaper
	{The computational complexity of Chinese and Italian noodle making}
	{Daniel M.\ Berry and Luisa Mich}
	{algorithm, Chinese mian, computational complexity, Italian pasta, noodle}
	{SIGBOVIK_2016_paper_2}
	{0cm}
	{}
\addreview{paper2review}{0cm}
\addpaper
	{Which ITG stepcharts are turniest?}
	{Ben Blum}
	{in, the, groove}
	{SIGBOVIK_2016_paper_12}
	{0cm}
	{\includegraphics[width=1in]{eval}}
\addreview{paper12eval}{0cm}

\addtrack{Lamb track}{Languages: Human and... Inhuman}
\addpaper
	{Lambda Doge: A digital canine language}
	{Joshua Suereth}
	{lambda calculus, doge, programming languages}
	{SIGBOVIK_2016_paper_15}
	{0cm}
	{}
\addpaper
	{Making the theoretical possible: the untyped $\lambda$-calculus in C++}
	{Jim McCann}
	{lambda, c++, c++11}
	{SIGBOVIK_2016_paper_23}
	{0cm}
	{}
\addpaper
	{A shortmantout}
	{David Renshaw and Jim McCann}
	{portmanteausteritycoon, hotshots, cathartichokes, sadjustment}
	{SIGBOVIK_2016_paper_13}
	{0cm}
	{}

\addtrack{Footpath track}{HyperLink to DnD}
\addpaper
	{The glEnd() of Zelda}
	{Dr.\ Tom Murphy VII Ph.D.}
	{small keys, boss keys, dungeon keys}
	{SIGBOVIK_2016_paper_16}
	{0cm}
	{}
\addpaper
	{Student success and sorrow: The determination of professor alignment and its effects on students}
	{D.\ Daly and E.\ Binns}
	{professors, academia, alignment}
	{SIGBOVIK_2016_paper_24}
	{0cm}
	{}

\addtrack{Garbage track}{Reduce, Reuse, Recycle}
\addpaper
	{PRESS RELEASE: FOR IMMEDIATE WORLDWIDE RELEASE}
	{Nicholas Fudala and Chester Francis}
	{editors note, this didnt seem very important, so we sat on it for 2 years, with love, the ach committee for retrocausal publication impact}
	{SIGBOVIK_2016_paper_17}
	{0cm}
	{}
\addpaper
	{Pittsburgh is a grid}
	{Stefan Muller}
	{Pittsburgh, grids, unnecessary integrals, computational geography}
	{SIGBOVIK_2016_paper_10}
	{0cm}
	{\includegraphics[width=1in]{eval}}
\addreview{paper10eval}{0cm}

\addtrack{Oversized track}{How (Over)fitting}
\addpaper
	{Reordering snacks is effective and just}
	{Dr.\ Tom Murphy VII Ph.D.}
	{snacking, permutations, comestability theory}
	{SIGBOVIK_2016_paper_8}
	{0cm}
	{}
\addpaper
	{0-order Non-linear ordinary differential equations}
	{Oscar I.\ Hernandez and Daniel J.\ Packer}
	{ordinary differential equations, non-linear, nonhomo}
	{SIGBOVIK_2016_paper_5}
	{0cm}
	{}
\addpaper
	{Deep spreadsheets with ExcelNet}
	{David Fouhey and Daniel Maturana}
	{deep learning, Excel, LibreOffice, convolutional neural network, spreadsheet}
	{SIGBOVIK_2016_paper_21}
	{0cm}
	{}
\addpaper
	{Sniffing for meaning: Defining and maximizing the signal-to-nose ratio}
	{Josh Cox}
	{signal, nose, ratio, sniff, smell, scent}
	{SIGBOVIK_2016_paper_22}
	{0cm}
	{}
\addreview{paper22review}{0cm}

\addtrack{Cattle track}{Higher-order Research}
\addpaper
	{On the topic of "um..."}
	{Timothy J.\ Parenti}
	{um, best, paper}
	{SIGBOVIK_2016_paper_20}
	{0cm}
	{}
\addreview{review-bestpaper}{0cm}
\addpaper
	{SMACK: When research in algorithms goes around in circles}
	{Patrick Lin and Weishuang Linda Xu}
	{algorithms, collider, particle physics}
	{SIGBOVIK_2016_paper_4}
	{0cm}
	{}
\addreview{review-smack}{0cm}
\addpaper
	{A look into the mind of the modern graduate student via telephonic obfuscation}
	{Erik Harpstead \textit{et al.}}
	{comestibility theory, telephonic obfuscation, computer human interaction}
	{SIGBOVIK_2016_paper_6}
	{0cm}
	{}
\addpaper
	{Dinner grant renewal request}
	{From Dr.\ Angus McNabb III to Jim McCann}
	{dinner, dog pictures, naps, napping, nap time, sleeping}
	{SIGBOVIK_2016_paper_14}
	{0cm}
	{}
\addpaper
	{Ode to reviewer two}
	{Anonymous}
	{ode, double-blind review, false politeness, landslide}
	{SIGBOVIK_2016_paper_7}
	{0cm}
	{}

>>>>

% TODO: Update heading
\addproceedings{ToC About Proceedings! Have We Got Papers for You!}

% TODO: Add reviews
% TODO: Add Avalon paper
% TODO: Substitute in new PC message
% TODO: Add ice skating photos?
% TODO: Change title page font

% TODO: Update track "numbering" scheme
\addtrack{Half-track}{Strong Accept}
\addpaper
	{Is this the shortest SIGBOVIK paper?}
	{Joe Doyle}
	{}
	{SIGBOVIK_2017_paper_14}
	{0cm}
	{}
\addpaper
	{I'm on vacation so I'm submitting a vacation picture instead of a paper, or, perhaps, a vacation photo in the format of a paper; I hope a predatory open access journal e-mails me about this article}
	{Jim McCann}
	{}
	{SIGBOVIK_2017_paper_15}
	{0cm}
	{}

\addtrack{Full track}{I'm Going to Use This!}
\addpaper
	{Who sorts the sorters?}
	{Alexander R.\ Frieder}
	{}
	{SIGBOVIK_2017_paper_39}
	{0cm}
	{}
\addpaper
	{Objectionability: A computational view of mathematical computation}
	{Cameron Wong and Dez Reed}
	{}
	{SIGBOVIK_2017_paper_18}
	{0cm}
	{}
\addpaper
	{Towards a well-defined and secure flirtation protocol}
	{Rowan Copley}
	{}
	{SIGBOVIK_2017_paper_72}
	{0cm}
	{}
\addpaper
	{A solution to the two-body problem}
	{Brandon Bohrer}
	{}
	{SIGBOVIK_2017_paper_29}
	{0cm}
	{}

\addtrack{Rototiller track}{Special Offers}
\addpaper
	{Call For Partners: Romance with rigor}
	{Brandon Bohrer}
	{}
	{SIGBOVIK_2017_paper_30}
	{0cm}
	{}
\addpaper
	{Nano electronic transplant in brain and eyes to analyze and process human thoughts and emotions}
	{Chinmaya Lele}
	{}
	{SIGBOVIK_2017_paper_66}
	{0cm}
	{}

\addtrack{Lamb track}{It's Only a Game Theory}
\addpaper
	{Dr.\ Boozehead, or How I learned to stop worrying and get drunk: Design principles and analysis of drinking games in the silicon age}
	{Kelvin M.\ Liu-Huang and Emily J.\ Simon}
	{}
	{SIGBOVIK_2017_paper_79}
	{0cm}
	{}
\addpaper
	{A boring follow-up paper to ``Which ITG stepcharts are turniest?'' titled, ``Which ITG stepcharts are crossoveriest and/or footswitchiest?''}
	{Ben Blum}
	{}
	{SIGBOVIK_2017_paper_63}
	{0cm}
	{}

\addtrack{Footpath track}{Nonstandard ML}
\addpaper
	{Batch normalization for improved DNN performance, my ass}
	{Joshua A.\ Wise}
	{}
	{SIGBOVIK_2017_paper_32}
	{0cm}
	{}
\addpaper
	{Colonel density estimation}
	{Harish Krishna \textit{et al.}}
	{}
	{SIGBOVIK_2017_paper_67}
	{0cm}
	{}
\addpaper
	{Degenerative adversarial networks}
	{Raphael Gontijo Lopes and Diptodip Deb}
	{}
	{SIGBOVIK_2017_paper_74}
	{0cm}
	{}
\addpaper
	{Stopping GAN violence: Generative unadversarial networks}
	{Samuel Albanie, S\'ebastien Ehrhardt, and Jo\~ao Henriques}
	{}
	{SIGBOVIK_2017_paper_13}
	{0cm}
	{}

\addtrack{Garbage track}{Putting the ``Under'' in ``Image Understanding''}
\addpaper
	{DeepDoggo: Learning the answer to ``Who's a good dog?''}
	{Benjamin J.\ Lengerich}
	{}
	{SIGBOVIK_2017_paper_69}
	{0cm}
	{}
\addpaper
	{$\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$ $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$ $\bigbox\bigbox\bigbox\bigbox$ $\bigbox\bigbox\bigbox\bigbox\bigbox$ $\bigbox\bigbox\bigbox\bigbox\bigbox$ $\bigbox\bigbox$ $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$}
	{$\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$ $\bigbox\bigbox\bigbox$ $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$ and $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$ $\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox\bigbox$}
	{}
	{SIGBOVIK_2017_paper_22}
	{0cm}
	{}
\addpaper
	{Distinguishing humans from other forms of cattle}
	{Boppity Bob Martinez and Flokkka\textdegree\ Haurilet}
	{}
	{SIGBOVIK_2017_paper_23}
	{0cm}
	{}

\addtrack{Oversized track}{New and ``Improved'' Languages}
\addpaper
	{On the Turing completeness of MS PowerPoint}
	{Tom Wildenhain}
	{}
	{SIGBOVIK_2017_paper_58}
	{0cm}
	{}
\addpaper
	{Effective multi-threading in Befunge}
	{Zachary Wade}
	{}
	{SIGBOVIK_2017_paper_37}
	{0cm}
	{}
\addpaper
	{Automatic distributed execution of LLVM code using SQL JIT compilation}
	{Mark Raasveldt, Tim Gubner, and Abe Wits}
	{}
	{SIGBOVIK_2017_paper_90}
	{0cm}
	{}
\addpaper
	{WysiScript: Programming via direct syntax highlighting}
	{William Gunther and Brian Kell}
	{}
	{SIGBOVIK_2017_paper_71}
	{0cm}
	{}
\addpaper
	{2M\~{}\~{} \# PRinty\# C with ABC!}
	{Dr.\ Tom Murphy VII, Ph.D.}
	{}
	{SIGBOVIK_2017_paper_73}
	{0cm}
	{}

\addtrack{Cattle track}{Debugging}
\addpaper
	{Amazon Web Services: Field observations related to arachnid cohabitation}
	{Riva Riley}
	{}
	{SIGBOVIK_2017_paper_60}
	{0cm}
	{}
\addpaper
	{Blackberry Debugging}
	{Allison M.\ Gardner and Kristen S.\ Gardner}
	{}
	{SIGBOVIK_2017_paper_40}
	{0cm}
	{}

\addtrack{TODO}{Impure Math and \textbackslash Big Data}
\addpaper
	{Fake news logic}
	{Will Nalls}
	{}
	{SIGBOVIK_2017_paper_91}
	{0cm}
	{}
\addpaper
	{RRR for UUU: Exact analysis of pee queue systems with perfect urinal etiquette}
	{Kristen Gardner and Ziv Scully}
	{}
	{SIGBOVIK_2017_paper_75}
	{0cm}
	{}
\addpaper
	{The next 700 type systems}
	{Carlo Angiuli}
	{}
	{SIGBOVIK_2017_paper_33}
	{0cm}
	{}
\addpaper
	{A modular approach to state-of-the-art big data visualization}
	{Keith A.\ Maki}
	{}
	{SIGBOVIK_2017_paper_78}
	{0cm}
	{}
\addpaper
	{Efficient computation of an optimal portmantout}
	{David Renshaw}
	{}
	{SIGBOVIK_2017_paper_34}
	{0cm}
	{}

\addtrack{TODO}{Talkin' Trash}
\addpaper
	{Garbage collection for heaps only a mother could love}
	{Your Parents}
	{}
	{SIGBOVIK_2017_paper_12}
	{0cm}
	{}
\addpaper
	{A new paradigm for robotic dust collection: Theorems, user studies, and a field study}
	{Rachel Holladay and Siddhartha S.\ Srinivasa}
	{}
	{SIGBOVIK_2017_paper_17}
	{0cm}
	{}

\addtrack{TODO}{Work-\texorpdfstring{\sout{stealing}}\ saving}
\addpaper
	{The Zero-color Theorem: An optimal poster design algorithm}
	{Michael Coblenz}
	{}
	{SIGBOVIK_2017_paper_11}
	{0cm}
	{}
\addpaper
	{Cerebral genus: Dead duck or phoenix?}
	{Oscar I.\ Hernandez}
	{}
	{SIGBOVIK_2017_paper_70}
	{0cm}
	{}
